---
title: "Part2 Analyzing ToothGrowth"
output: html_document
---
#### By Zoey Phay

#### Overview
For the second part, we're going to analyze the ToothGrowth data in the R datasets package.

The dataset records Vitamin C effects on the tooth growth on guinea pigs at different dosage (0.5,1 and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

A data frame with 60 observations on 3 variables.

len numeric Tooth length
supp factor Supplement type (VC or OJ).
dose numeric Dose in milligrams.

#### Load the ToothGrowth data and perform some basic exploratory data analyses
```{r,echo=TRUE}
library(ggplot2)
library(datasets)
data(ToothGrowth)
head(ToothGrowth)
```
```{r,echo=TRUE}
str(ToothGrowth)
```

#### Provide a basic summary of the data.
```{r,echo=TRUE}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
table(ToothGrowth$supp, ToothGrowth$dose)
summary(ToothGrowth)
```
```{r,echo=TRUE}
mean(ToothGrowth$len) # mean
```
```{r,echo=TRUE}
sd(ToothGrowth$len) # standard deviation
```
Graph it..
```{r,echo=TRUE}
ggplot(ToothGrowth, aes(x=factor(dose),y=len,fill=factor(dose))) + geom_boxplot(notch=F) + facet_grid(.~supp) +
     scale_x_discrete("Dosage (Milligram)") +   
     scale_y_continuous("Length of Teeth") +  
     ggtitle("Effect of Dosage and Supplement Type on Tooth Growth")
```

#### Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose
```{r,echo=TRUE}
supp.t1 <- t.test(len~supp, paired=F, var.equal=T, data=ToothGrowth)
supp.t2 <- t.test(len~supp, paired=F, var.equal=F, data=ToothGrowth)
supp.result <- data.frame("p-value"=c(supp.t1$p.value, supp.t2$p.value),
                          "Conf-Low"=c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High"=c(supp.t1$conf[2],supp.t2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
supp.result
```

#### State conclusions and the assumptions needed. 

Assumptions:
Guinea pigs were randomly chosen (same population variance); Samples are independent (sample data not paired)

Conclusion:
1. Orange juice results more tooth growth than ascorbic acid, at 0.5 and 1 dosages.
2. Tooth growth is not significantly different for the different delivery method at 2 mg.
3. Dosage plays the key role in tooth growth 


